Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-09 paper.tex
Adding response to HMF comment and added a line in the paper.

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. These stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.

>>>>

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. \textbf{At this time, $z = 27$, there are only 6 halos that are above our mass resolution limit.} These \textbf{Pop III} stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.

### 2019-10-09 referee.tex
Adding response to HMF comment and added a line in the paper.

-The HMF at z=20 is overshooting the analytic estimate. Need to get together with John to see why.

\jhw{We are still investigating this issue. Calculate the matter power spectrum and compare with the analytic expectation to see if the simulation was initialized with some odd mode.}

>>>>

At the time of the first star formation, our simulation only marginally resolves the smallest main halos, there is only a total of 6 halos above our resolution limit of $10^{5} M_{\odot}$. Because of this, there are not enough halos to accurately represent the HMF at that time, which is why we have not added that to Figure 2. We have added this detail to the first paragraph of the Results section.
